```{r}
library(readxl)
```

Task 01
Outlier detection applying k-means clustering
Data set: learning.xlsx 

A data set learning2 is given.
Run a "Cluster Based" outlier detection applying k-means clustering after Barai & Dey (2017)3
Calculate solutions of two different numbers of clusters.
x = 3 and x = 4 in kmeans(datas, centers = x, nstart = 10)4
How can the solutions be interpreted?
```{r}
# Load data in
learning <- read_excel("learning.xlsx")

# Explore data 
head(learning, n = 10)
```
Visualisation

```{r}
plot(learning$success, learning$effort)
boxplot(learning)
```
Scale Data - Visualisation
```{r}
data <- scale(learning, center = FALSE, scale = TRUE)
boxplot(data)
plot(data)
```

Cluster Analysis - 4
```{r}
km_4 <- kmeans(data, centers = 4, nstart = 10)
groups_km_4 <- km_4$cluster
plot(data, pch = groups_km_4, col=groups_km_4, lwd=2)
legend("topright", legend = 1:4, pch = 1:4, col=1:4, bty = "n")
```
Cluster - Analysis 3 Clusters 
```{r}
km_3 <- kmeans(data, centers = 3, nstart = 10)
groups_km_3 <- km_3$cluster
plot(data, pch = groups_km_3, col=groups_km_3, lwd=2)
legend("topright", legend = 1:3, pch = 1:3, col=1:3, bty = "n")
```
 With k = 3, k-means identifies three broad groups of students: a low effort and low-success group, a medium effort and medium to high effort and high success group, and lastly a high effort and low success group.

With k = 4, the algorithm splits the medium to high effort group into two distinct subgroups: high effort and high success and medium effort and high success. This provides a more nuanced understanding of performance, highlighting that students who invest similar levels of effort may achieve very different outcomes.

Therefore, k = 4 offers a more detailed structure, clearly separating the clusters and showing the differences whereas k = 3 provides a simpler but less detailed representation.
