Task 01

The body weight of individuals interviewed in the HSE1 is considered.
Data set → HSE.xlsx
The variable for the body weight is wtval measured in kilograms.
Using R, generate a boxplot broken down by gender (variable sex).
How can the boxplot be interpreted?

Library
```{r}
library(readxl)
```

Loading data 
```{r}
# Load data
df.body.weight <- read_excel("HSE.xlsx")

# Inspect data
head(df.body.weight)

# Inspect unique values of Sex
unique(df.body.weight$sex)
```
Plot
```{r}
boxplot(wtval ~ sex, data = df.body.weight, 
        main = "Body weight by Sex", 
        xlab = "Sex",
        ylab = "Body weight", 
        col = c("lightblue", "lightpink"))
```
Interpretation: The boxplot shows the distribution of body weight by sex. Both groups Sex 1 and Sex 2 display similar variability in their data. However, Sex 1 showa a higher median body weight than Sex 2, suggesting that individuals in Sex 1 generally have a higher body weight on average.

The body weight range for Sex 1 extends approximately from 50 kg to 120 kg, whereas Sex 2 ranges from about 20 kg to 100 kg. Sex 1 also shows a larger number of outliers, with extreme values both at the lower end around 30–50 kg and the upper end around 120–170 kg. Whereas, Sex 2 shows fewer outliers only on the higher end around 100–180 kg.

Both sexes seem to be right skewed. 

Overall, the plot suggests that Sex 1 tends to have higher body weights and more extreme values compared to Sex 2. 


Histogram to confirm distribution
```{r}
# Split data into separate subsets
HSE_m <- subset(df.body.weight, sex == 1)
HSE_f <- subset(df.body.weight, sex == 2)

# Create Histograms
hist(HSE_m$wtval, main = "Body Weight Distribution for Men", xlab = "Men")
hist(HSE_f$wtval, main = "Body Weight Distribution for Women", xlab = "Women")
```
This confirms the assumption that the distributions of both men and women are rightskewed. 

Task 02
```{r}
# Load Data
task.02 <- read_excel("task_02.xlsx")

# Inspect data 
head(task.02)
```

Boxplots 
Boxplot Variable A
```{r}
# Boxplot for Variable A
boxplot(x = task.02$Variable_A, main = "Boxplot for Variable A", 
        xlab = "Variable A")
```
Boxplot Variable B
```{r}
#Box plot for Variable B
boxplot(x = task.02$Variable_B, main = "Boxplot for Variable B", 
        xlab = "Variable B")
```
Box plot Variable C
```{r}
# Box plot for Variable C
boxplot(x = task.02$Variable_C, main = "Boxplot for Variable C", 
        xlab = "Variable C")
```

Histograms 
Variable A
```{r}
# Histogram distribution Variable A
hist(x = task.02$Variable_A)
```
Variable B 
```{r}
hist(x = task.02$Variable_B)
```
Variable C
```{r}
hist(x = task.02$Variable_C)
```
The histogtams confirm our conclusions. s
